---
title: "Toolik Station Air Temperature"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(here)
library(janitor)
library(skimr)
```

## Read in the Toolik Lake meteorologic data

**Data:** Shaver, G. 2019. A multi-year DAILY weather file for the Toolik Field Station at Toolik Lake, AK starting 1988 to present. ver 4. Environmental Data Initiative. https://doi.org/10.6073/pasta/ce0f300cdf87ec002909012abefd9c5c (Accessed 2021-08-08).

The data are stored in the `data-raw` subfolder. We'll use `here::here()` to point to it, and read it in using the `readr::read_csv()` function from the `readr` package (part of the `tidyverse`). 

```{r}
toolik_weather <- read_csv(here("data", "data-raw", "toolik_weather.csv"), na = ("#N/A")) %>%
  clean_names()

# What is this %>% thing? Meet the pipe operator! Also, as of a couple months ago, |> is a native pipe operator (versus %>%, which comes along with the tidyverse)

# Now what are the column names?
```

```{r}
names(toolik_weather)
```


- First: Look at the data you've read in (always always)

- Second: What is that warning? `problems()` - line 6424

- How does R assign classes to data it reads in? See: https://readr.tidyverse.org/articles/readr.html

- Third: Are all missing values stored the same way? See: #N/A, and add a new argument within `readr`: na = "#N/A"


## Basic exploration

```{r}
# An overview:
skimr::skim(toolik_weather)

# A few other things to explore
dim(toolik_weather)
names(toolik_weather)
```


## Make a graph

Let's make a jitterplot of temperatures by month. 

```{r}
toolik_plot_mine <- ggplot(toolik_weather, aes(x = as.factor(month), y = daily_air_temp_mean_c, color = daily_air_temp_mean_c)) +
  geom_jitter(show.legend = FALSE) +
  scale_color_gradient(low = "darkgreen", high = "lightblue") +
  labs(title = "Toolik Station daily air temperature",
       x = "Month",
       y = "Daily mean air temperature (Celsius)") +
  theme_linedraw()

toolik_plot_mine
```


```{r}
# toolik_temp_plot <- ggplot(data = toolik_weather, aes(x = as.factor(month), y = daily_air_temp_mean_c)) +
#   geom_jitter(aes(color = daily_air_temp_mean_c), show.legend = FALSE) +
#   scale_color_gradient(low = "blue", high = "orange") +
#   theme_minimal() +
#   labs(title = "Toolik Station daily air temperature",
#        x = "Month",
#        y = "Daily mean air temperatures (Celsius)")
# 
# toolik_temp_plot
```

## Export a figure

```{r}
# ggsave(here::here("figs", "toolik_temp_plot.png"), height = 6, width = 7)
ggsave(here::here("figs", "toolik_plot_mine.png"), plot = toolik_plot_mine, height = 6, width = 7)
```

Now try changing something about the ggplot code, and re-run your `ggsave()` line above. Does your saved figure change? Great! 

## End Example 1
